CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

```{r testing}
# Hypothesis testing  
df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, BPPARAM=SnowParam(18)) 
```

>>>>

```{r testing}
# Hypothesis testing      
df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA)#, BPPARAM=SnowParam(18)) 
```
